04-Data-Analysis

### 2021-04-19 00-Data-Processing/00-Data-Processing-for-Food-Banks-Accessibility.Rmd
Update food bank and routing code
Changes related to updating the food banks csv with more info used to filter sites

Read file with locations:
```{r}
foodbank_locations <- read_csv("input-data-files/foodbanks-hamilton.csv",
                               col_types = cols(ID = col_double(),
                                    NAME = col_character(),
                                    TYPE = col_character(),
                                    ADDRESS = col_character(),
                                    COVIDClose = col_double(),
                                    latitude = col_double(),
                                    longitude = col_double(),
                                    name = col_character(),
                                    desc = col_character(),
                                    source = col_character(),
                                    precision = col_character()
                               ))
```

COVIDClose is an indicator variable for whether this bank closed during the pandemic. Convert to factor:
```{r}
foodbank_locations <- foodbank_locations %>%
  mutate(COVIDClose = replace_na(COVIDClose, 0),
         COVIDClose = factor(COVIDClose,
                             levels = c(0, 1),
                             labels = c("No", "Yes")))
```

Convert to simple features:
```{r}
foodbank_locations <- foodbank_locations %>%
  st_as_sf(coords = c("longitude", "latitude"), 
           crs = 4326) %>%
  st_transform(crs = 26917)
```

@@

### `dwelling_network_points_2016.RData`

>>>>

Read file with locations:
```{r}
foodbank_locations <- read_csv("input-data-files/foodbanks-hamilton.csv",
                               col_types = cols(ID = col_double(),
                                    NAME = col_character(),
                                    TYPE = col_character(),
                                    ADDRESS = col_character(),
                                    STATUS = col_character(),
                                    latitude = col_double(),
                                    longitude = col_double(),
                                    name = col_character(),
                                    desc = col_character(),
                                    source = col_character(),
                                    precision = col_character()
                               ))
```

COVIDClose is an indicator variable for whether this bank closed during the pandemic. Convert to factor:
```{r}
foodbank_locations <- foodbank_locations %>%
  mutate(STATUS = replace_na(STATUS, "Open"),
         COVIDClose = if_else(STATUS == "Cancelled", true = "Yes", false = "No")) %>%

  # filter out Meals on Wheels, Student Nutrition programs, Shopping and Transportation, & Good Food Box Programs
  filter(TYPE %in% c("Community Kitchen", "Congregate Dining", "Community Meals", "Food Banks", "Free Meals", "Low Cost Meals"))
```

Convert to simple features:
```{r message = FALSE}
foodbank_locations <- foodbank_locations %>%
  st_as_sf(coords = c("longitude", "latitude"), 
           crs = 4326) %>%
  #st_transform(crs = 26917) %>%

  # filter out points beyond the Hamilton CMA (there's one point in Brantford)
  filter(st_intersects(x = geometry, y = hamilton_cma, sparse = FALSE))
```

@@

### Origin parcel locations

### 2021-04-19 00-Data-Processing/04-Data-Analysis.Rmd
Update food bank and routing code
Changes related to updating the food banks csv with more info used to filter sites

Join the pharmacy data to the travel time matrices:
```{r}
ttm_car <- ttm_car %>%
  left_join(foodbank_locations %>%
              st_drop_geometry() %>%
              dplyr::select(ID, 
                            COVIDClose),
            by = c("OBJECTID" = "ID"))

>>>>

Join the food bank data to the travel time matrices:
```{r}
ttm_car <- ttm_car %>%
  left_join(foodbank_locations %>%
              st_drop_geometry() %>%
              dplyr::select(ID, 
                            COVIDClose),
            by = c("OBJECTID" = "ID"))
